# Results

```{r descriptive-statistics, echo=FALSE}
# get descriptive statistics for each group -----------------------------------
descriptive_statistics_table <- df_ind_t.test %>%
  group_by(IV) %>%
  summarise(n = dplyr::n(),
            Mean = mean(DV),
            Variance = sd(DV)^2,
            SD = sd(DV),
            SE = sd(DV)/sqrt(dplyr::n()),
            CI.lower = mean(DV) - (abs(qnorm((1-0.95)/2)) * sd(DV)/sqrt(dplyr::n())),
            CI.upper = mean(DV) + (abs(qnorm((1-0.95)/2)) * sd(DV)/sqrt(dplyr::n()))
            )
descriptive_statistics <- purrr::transpose(dplyr::select(descriptive_statistics_table, !IV))
names(descriptive_statistics) <- descriptive_statistics_table$IV

# get summary statistics for the entire sample --------------------------------
summary_statistics_G <- df_ind_t.test %>%
  summarise(N = nrow(.),
            Grand.Mean = mean(DV),
            Grand.Variance = sd(DV)^2,
            Grand.SD = sd(DV),
            Grand.SE = sd(DV)/sqrt(nrow(.)),
            Grand.CI.lower = mean(DV) - (abs(qnorm((1-0.95)/2)) * sd(DV)/sqrt(nrow(.))),
            Grand.CI.upper = mean(DV) + (abs(qnorm((1-0.95)/2)) * sd(DV)/sqrt(nrow(.)))
            ) %>%
  as.list()
```

```{r run-ttest}
# run ttest
model <- t.test(DV ~ IV, data = df_ind_t.test)
# get effect size
model_effsize <- effectsize::cohens_d(DV ~ IV, data = df_ind_t.test)$Cohens_d
# set the significance level for the omnibus ANOVA
sig_level <- 0.05
# test significance
model_p.value <- broom::tidy(model)$p.value
model_significance <- model_p.value < sig_level

# PRINTING --------------------------------------------------------------------
# concatenate omnibus ANOVA and effect sizes into an APA string
print_model <- paste0(papaja::apa_print(model)$statistic, ", $d = ",
                      sprintf("%.2f", round(model_effsize, 2)), "$")
```

An independent t-test was used to test the hypothesis that participants in group A had significantly higher scores on the dependent variable than participants in group B. Results of the t-test show that the hypothesis was supported, with scores in group A ($M = `r papaja::printnum(descriptive_statistics$A$Mean)`$, $SD = `r papaja::printnum(descriptive_statistics$A$SD)`$) being significantly higher than scores in group B ($M = `r papaja::printnum(descriptive_statistics$B$Mean)`)$, $SD = `r papaja::printnum(descriptive_statistics$B$SD)`$), `r print_model`.
